Scaling rates of true polar wander in convecting planets and moons

### 2017-09-11 tpw_rate.tex
Add clarifying clause.

Figure~\ref{fig:misfit} shows a representative time series from the convection calculations. As before, we compute the convective moment of inertia in the geographic frame and evaluate the eigenvalues of $\mathbf{E}$ to determine the eigengap. We also evolve the orientation of the rotation axis by integrating  Equation~\eqref{eq:liouville_ode} in time.
Since it is a 2D model, the spin axis is described by a single angle. The misalignment angle $\theta$ also lies in the plane of the 2D model.
When the eigengap gets small,  the corresponding misalignment angle increases and the rate of polar wander becomes much faster. This behavior is consistent with the predictions from Equation (33). We draw special attention to two events in the time series. At $\sim$0.3 Gyr the eigengap dips and the misalignment angle increases to $\theta \sim 20^{\circ}$. There is a large change in the orientation of the spin axis, even though
there is technically no interchange of the maximum and intermediate axes. A conventional IITPW event occurs at $\sim 1$ Gyr;  the eigengap goes to zero, interchanging the maximum and intermediate axes. The misfit angle goes to approximately $90^\circ$. During this time the orientation of the spin axis changes by roughly 90$^{\circ}$.

>>>>

Figure~\ref{fig:misfit} shows a representative time series from the convection calculations. As before, we compute the convective moment of inertia in the geographic frame and evaluate the eigenvalues of $\mathbf{E}$ to determine the eigengap. We also evolve the orientation of the rotation axis by integrating  Equation~\eqref{eq:liouville_ode} in time.
Since it is a 2D model, the spin axis is described by a single angle. The misalignment angle $\theta$ also lies in the plane of the 2D model.
When the eigengap gets small,  the corresponding misalignment angle increases.
Even though at that moment the driving force may be small,
it can recover quickly due to convection, and the rate of polar wander becomes much faster.
This behavior is consistent with the predictions from Equation (33). We draw special attention to two events in the time series. At $\sim$0.3 Gyr the eigengap dips and the misalignment angle increases to $\theta \sim 20^{\circ}$. There is a large change in the orientation of the spin axis, even though
there is technically no interchange of the maximum and intermediate axes. A conventional IITPW event occurs at $\sim 1$ Gyr;  the eigengap goes to zero, interchanging the maximum and intermediate axes. The misfit angle goes to approximately $90^\circ$. During this time the orientation of the spin axis changes by roughly 90$^{\circ}$.
